environmental_data_preperation

### 2018-09-20 src/environmental_data_preperation.Rmd
export unique grid as polygon

now give a unique ID to each cell
```{r}
unique_cell[unique_cell > 0] <- 1:6731 
writeRaster(unique_cell,'../output/env/unique_cell.tif',overwrite=TRUE, options=c('TFW=YES')) #so you can access it again
```

>>>>

now give a unique ID to each cell
```{r}
unique_cell[unique_cell > 0] <- 1:6731 
writeRaster(unique_cell,'../output/env/unique_cell.tif',overwrite=TRUE, options=c('TFW=YES')) #so you can access it again
uniquecell_poly <- rasterToPolygons(aea[[1]], fun=NULL, n=4, na.rm=TRUE, digits=12, dissolve=FALSE)

writeOGR(uniquecell_poly, dsn = '.', layer = '../output/env/poly', driver = "ESRI Shapefile")
